---
title: "Brodeur-2018"
---

# Motivation 

The motivation section responds to the following questions: 

* Why is the research question relevant?
* What are the main hypothesis?

First, the research question is relevant because understanding the impact of terror attacks on employement isn't well established.
Indeed, the data available to answer such question (subnational data) has only been collected in the recent years.
Secondly,  The difficult of the topic as well as the different channels make answering this question challenging and no consensus has been established yet.
According to Mill (1848), nations should recover question when the direct impact on productive capital isn't substantial,
while Becker and Murphy (2001) argues that the uncertainty about futur terror attacks makes their effect hard to estimate.

Thirdly and most importantly, (percieved) costs of terror attacks are huge.
Understand such impacts would benefit countries where terror attacks are proeminent,
such as the United States of America, where the paper has been conducted.

More specifically, the paper investigates the direct impact of terror attacks on employement trough
* Employement rate,
  - General, through "100 x Log Employment (per capita)"
  - Industry-wise, trough
    * 100 x Log Manufacturing Employment (per capita)
    * 100 x Log Construction Employment (per capita)
    * 100 x Log Retail Employment (per capita)
    * 100 x Log Wholesale Employment (per capita)
    * 100 x Log Services Employment (per capita)
    * 100 x Log Finance Employment (per capita)
* Earning (locall, at the country scale), through
  - 100 x Log Real Earnings (per capita)
  - 100 x Log Real Earnings per Job

as well as through potential channels, such as 
* Destruciton of human and physiacal capital
* Consumer and investment behavior
* Housing Market
* Migration
* Counterterrorism expenditures



## Answers:
1. Difficult topic, no consensus yet and interesting application prospects for states and country.

**2. Hypothesis**

Effects of TA on local employement is ambiguous to the many channels at work.

We expect an effect of terror attacks (TA) on human and physical capital, as most TA are of small scale.

We expect an effect of TA on consumer and investement behavior, through increased uncertainty.

We expect an effect of TA on the housing market, as a decrease of housing prices following a TA is well-documented.

We expect an effect of TA on migration, as a TA worsen individual's living and working conditions.

We expect an small effect of TA on counterterrorism expenditures, through moving ressources from productive sector to undproductive sector (security,...).
Additionally, as counterterrorism expenditures are generaly at the federal and regional level, is it unclear if local (county) economy would affected would affected.

# Data sources

This section responds to the following question: 

* Where does the data come from (country, time period, source).
* What are the key variables?
* How are those variable measured?

First important source is the Global Terrorism Database (2017), firstly established a counselling company, Pinkerton Global Intelligence Services, and now maintained by 
the National Consortium for the Study of Terrorism and Responses to Terrorism (START).
Time period is 1970 to 2013. 1993 is missing because the box of data fell out of a truck during transit.
Information sources are media articles, electronics news archive, and other existing datasets.
Variable measurement is unkown, probably 'manual'.
Main variables are 
  - date,
  - location (at the county level)
  - description of each terror attack, allowing for cross-matching with other dataset with other datasets
  - attack type (governement buildings, businesses, ...)
  - weapons type (biological, explosives, incendiary, ...)
  - number of deaths
  - number of injured people
  - property dammage

**Note**, the SUCESSFULL variable was constructed using this dataset

Second important dataset is Country Business Patterns (CBD) datasets, coming form the Business Register, maintained by the US Census Bureau.
Time period is 1970 to 2013.
Information sources is administrative data for single estabilshments, and Economic Census + Company Organization Survey for multi-establishement firm is administrative data for single estabilshments, and Economic Census + Company Organization Survey for multi-establishement firms.
Variable measurement is then admininstrative or survey.
Main variables are:
  - number of establishements
  - establishement location
  - employement during the middle of March
  - quarter payroll
  - annual payroll

**Note**, Governement, military employement, rail transportation, household employement industries are present.

An additionnal datasets was used to compare finding and test their robustness, the Bureau of Economic Analysis (BEA).
Main Variables:
- Number of jobs in a country

Governement and military employement were added to facility comparison.

**Note** unpaid family workers and volunteers are counted.

# Method

This section responds to the following questions:

* What are teh assumptions of the method
* Are those assumptions plausible in this example?

The targetted analysis of the project is the Difference-in-Difference Method.
This method has the following assumptions: 

1. Stable Unit Treatment Value Assumption (SUTVA)
2. Treatment randomness assignement
3. Parallel Trend Assumption
4. Exogeneity, which is often implies the *3.* holds.

## SUTVA

Bordeur tests for spillover effects by aggregating to broader Census regions (9 divisions).
'Division' is not a cofounder for employement rate and SUCCESSFUL

Additionnaly, he tests local spill-over effects by testing the effects of the successfull TA on neighboring counties.
He found neglibile and idiosyncratic effects, hence this assumption is respected.

## Treatment randomness assignement

Is the successfulness of an attack predictable or can we anticipate it?
This is likely not the case since the sample of county-year observation hosting successful and failed terror
are balanced across a void range of characteristics.

Additionnaly, given a particular location, the successfulness or failure of a TA can be considered random.

**Remark**, this link back to the Parallel Trend Assumption

## Parallel Trend Assumption

```{r}
#| label: Year of event

# Step 1: Get the event year (first 0->1 edge in post) and success status for each county.
ev_info <- df %>%
  arrange(fips, year) %>%
  group_by(fips) %>%
  mutate(is_event_year = (post == 0) & lead(post) == 1) %>%
  summarise(
    event_year  = if (any(is_event_year, na.rm = TRUE)) min(year[is_event_year],
                                                 na.rm = TRUE) else NA_integer_,
    is_success  = if (any(is_event_year, na.rm = TRUE)) as.integer(any(
         successful1[is_event_year] == 1, na.rm = TRUE)) else NA_integer_) %>%
  ungroup()

df_es <- df %>%
  left_join(ev_info, by = "fips") %>%
  filter(!is.na(event_year)) %>%  # keep only fips with an event
  mutate(event_time = year - event_year)

df_es_win <- df_es %>% filter(event_time >= -3, event_time <= 3)

```

#### Plot to check parallel trend assumption

```{r}
#| label: iPlot
#| message: false

es_mod <- feols(
  ln_emp_pop ~ i(event_time, is_success, ref = -1) | fips + year,
  cluster = ~ fips,
  data = df_es_win)

iplot(es_mod,
      main = "Event study (successful vs failed): parallel-trend check",
      xlab = "Years relative to event (ref = -1)",
      ref.line = 0)
      
# tidy_es <- broom::tidy(es_mod, conf.int = TRUE) %>%
#   filter(str_detect(term, "^event_time::")) %>%
#   mutate(event_time = as.numeric(str_match(term, "event_time::(-?\\d+)")[,2]))

# 
# ggplot(tidy_es, aes(event_time, estimate)) +
#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
#   geom_point() +
#   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .2) +
#   labs(title = "Event study (successful − failed): parallel-trend check",
#        x = "Years relative to event (ref = −1)",
#        y = "Diff-in-diff effect on ln_emp_pop") +
#   theme_minimal()

```

#### Interpretation

The pre-treatment coefficients (t = −3, −2) are close to zero and statistically indistinguishable from zero, supporting the parallel trend assumption.

Starting from t = +1, coefficients turn negative, suggesting that counties experiencing a successful attack face lower employment growth relative to counties with failed attacks, although estimates are imprecisely estimated.

## Exogeneity

Brodeur includes year fixed effects (absorbing nationwide shocks such as recessions) and month fixed effects (seasonality)
He also includes county fixed effects absorbing time-invariant county heterogeneity.
Together, these control for common macro shocks.

He also add condition the analysis on common possible covariate to avoid cofounder effects, such as 
the attack type of the weapon type.

# Descriptive Statistics

# Results

This section responds to the following questions:

* What are the main results
* Are they plausible?
* How robust the result are to changing samples?

## Result of the basic model:

**log(job/pop) ~ SUCCESS + n_attacks | year+month+county:**

The first important information is that effect of fixed-effects variable are not significant.
There is a significant dip of 1% after a TA on job/population.
Such effect is significant for first 2 years following a TA.

**log(job/pop) ~ SUCCESS + n_attacks + attack_type + weapon_type | year + month + county:**


No real change from the previous model without attack type and weapon type.
Drop of log(job/(population)) between 0.9 to 1.4%

**log(real earning per capita) ~SUCCESS + n_attacks + attack_type + weapon_type | year + month + county**

Estimates are positives before the attacks and negative after, droping by 1 to 3%.
Those effects are significant at the 1% level.

## Difference-in-Difference Model

$$
Y_{c,t} = \alpha + \eta * SUCESSFULL_{c,t} + \zeta * POST_{c,t} + \gamma * X'_{c, t} + \theta_c + \delta_t + \epsilon_{c,t}
$$

Dependant variable is $100 * log(job/capita)$

### Job/capita

**First Model**

$$
Y_{c,t} = \alpha + \eta + \zeta * POST_{c,t} + \theta_c + \delta_t + \epsilon_{c,t}
$$

Significant effect of $POST$ at the 1% significant level.
This suggest that the attemps of an attack itself, and not necessarily its success,
drives employement down.

**Second Model**

$$
Y_{c,t} = \alpha + \eta * SUCESSFULL_{c,t} + \zeta * POST_{c,t} + \theta_c + \delta_t + \epsilon_{c,t}
$$

Direct comparison with the first model but including the SUCESSFUL variable.
Sucessful TA reduce employement by 2%, effect statistically significant at the 5% level.

**Third to Six Model**

Variable such as 'non-american' target and 'logistically international',
as well as another variable absorbing employement shocks are statistically significant at the 5% level.

#### Plausibility

There is a significant negative effect of successfulness of an attack on job/capita.
The standard error a half as high as the estimate, indicating confidence in that the estimate is close to the true estimateThe standard error a half as high as the estimate, indicating confidence in that the estimate is close to the true estimate.
### Earnings per capita

Dependent variable: 100 * log(earnings/capita)

SUCCESSFUL has an effect at conventional level (10%). Hence, debatable.

#### Plausibility

10% significance levels is small. However, standard errors are half as big as the estimates, indicating that the estimates is relatively close to the true SUCCESSFUL estimates.

### Earnings per jobs

No effect at the 10% levels, hence 'effect' of aggregated earnings but not per jobs.
Could there be a covariate explaining this?

#### Plausibility 

A significant effect on the 10% level is debatable.
Additionnaly, the effect on aggregated earnings but not per job means there is likely a covariate involved.
Hence the result aren't really plausible.

# Conclusion

This section responds to the following questions:

* How do you replication results copamre to the results of the research paper?
* Are there similar studies and how do your results
compare to these results?
