---
title: "Brodeur-2018"
format: html
---

## Libraries and data loading

Load libraries.

```{r}
#| label: libraries
#| message: false

library(tidyverse)
library(fixest)
library(knitr)
library(htmltools)

```

Load data.

```{r}
#| label: dataload
#| message: false

load("C:/Users/dhub1/RStudioProjects/Brodeur-2018/Brodeur (2018).RData")
variable_table <- read_csv("variable_table.csv")
```

Check data (in Console) and open variable_table

```{r}
#| label: datacheck
#| include: false

str(df)
glimpse(df)
summary(df)
# View(variable_table)
# View(df)
df %>%
  summarise(
    n_years = n_distinct(year),
    n_fips  = n_distinct(fips)
    )

```

## Replication of Figure 1

```{r}
#| label: figure1

# identify years with attack(s) within fips
attack_years <- df %>%
  arrange(fips, year) %>%
  group_by(fips) %>%
  mutate(
    lead_post      = dplyr::lead(post),
    is_attack_year = (post == 0) & (lead_post == 1)
  ) %>%
  ungroup() %>%
  filter(is_attack_year)

# number of events
yearly_table <- attack_years %>%
  group_by(year, successful1) %>%
  summarise(count_events = sum(meventperyear), na.rm = TRUE, .groups = "drop") %>%
  # for ggplot color scale
  mutate(successful1 = as.character(successful1)) %>%
  arrange(year, successful1)

# the plot
ggplot(yearly_table, aes(x = year, y = count_events, color = factor(successful1))) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  scale_color_manual(
    values = c("0" = "#2ECC71", "1" = "#E74C3C"),
    labels = c("0" = "failed", "1" = "successful"),
    breaks = c("1", "0")
  ) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(
    title = "Figure 1: Number of counties with successful or failed attacks",
    x = "Jahr",
    y = "Number of counties",
    color = "Attack",
    caption = "Brodeur 2018: his Figure 1 is similar but with different numbers"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12, hjust = 0.5),
    axis.title = element_text(size = 10),
    legend.position = "bottom"
  )

```

## Replication of table 6

### Create the models

```{r}
#| label: table6Models
#| message: false

df_sub <- df %>%
  filter(!is.na(successful))

# Panel A – Brodeur Table 6
m6A1 <- feols(
  ln_emp_pop ~ post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m6A2 <- feols(
  ln_emp_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m6A3 <- feols(
  ln_emp_pop ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l,
  cluster = ~fips, data = df_sub
)

m6A4 <- feols(
  ln_emp_pop ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m6A5 <- feols(
  ln_emp_pop ~ successful + post + meventperyear |
    fips + month^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m6A6 <- feols(
  ln_emp_pop ~ successful + post + meventperyear |
    fips + month^year + div_9_all^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)


# Panel B
m6B1 <- feols(
  ln_real_qp1_pop ~ post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m6B2 <- feols(
  ln_real_qp1_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m6B3 <- feols(
  ln_real_qp1_pop ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l,
  cluster = ~fips, data = df_sub
)

m6B4 <- feols(
  ln_real_qp1_pop ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m6B5 <- feols(
  ln_real_qp1_pop ~ successful + post + meventperyear |
    fips + month^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m6B6 <- feols(
  ln_real_qp1_pop ~ successful + post + meventperyear |
    fips + month^year + div_9_all^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)


# Panel C
m6C1 <- feols(
  ln_real_qp1_job ~ post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m6C2 <- feols(
  ln_real_qp1_job ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m6C3 <- feols(
  ln_real_qp1_job ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l,
  cluster = ~fips, data = df_sub
)

m6C4 <- feols(
  ln_real_qp1_job ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m6C5 <- feols(
  ln_real_qp1_job ~ successful + post + meventperyear |
    fips + month^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m6C6 <- feols(
  ln_real_qp1_job ~ successful + post + meventperyear |
    fips + month^year + div_9_all^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

```

### Create table 6

```{r}
#| label: tableCommons

# define common table properties
dict_common <- c(
  post = "Post-attack",
  successful = "Successful attack",
  meventperyear = "Multiple events per year",
  non_us_t = "Non-US target",
  int_l = "International attack",
  aa_assass = "Assassination",
  aa_armed = "Armed assault",
  aa_bomb = "Bombing",
  aa_facility = "Facility attack",
  ww_firearm = "Firearm",
  ww_explo = "Explosives",
  ww_incend = "Incendiary"
)

order_common <- c(
  "%successful", "%post", "%meventperyear",
  "%non_us_t", "%int_l",
  "%aa_assass", "%aa_armed", "%aa_bomb", "%aa_facility",
  "%ww_firearm", "%ww_explo", "%ww_incend"
)

```

#### Table 6, Panel A: Employment (ln_emp_pop)

```{r}
#| label: Table6PanelA
#| message: false

tab6A <- etable(list(m6A1, m6A2, m6A3, m6A4, m6A5, m6A6),
       se.below = TRUE,
       signif.code = c("***"=0.01,"**"=0.05,"*"=0.10," "=1),
       dict = dict_common, order = order_common, digits = 3,
       drop = "Intercept", fitstat = ~n + r2, tex = FALSE)

## for rendering: knitr...  for interactive: html_print...
# knitr::kable(tab6A, format = "pipe")
html_print(HTML(kable(tab6A, "html")))

```

#### Table 6, Panel B: Earnings (ln_real_qp1_pop)

```{r}
#| label: Table6PanelB
#| message: false

tab6B <- etable(list(m6B1, m6B2, m6B3, m6B4, m6B5, m6B6),
       se.below = TRUE,
       signif.code = c("***"=0.01,"**"=0.05,"*"=0.10," "=1),
       dict = dict_common, order = order_common, digits = 3,
       drop = "Intercept", fitstat = ~n + r2, tex = FALSE)

## for rendering: knitr...  for interactive: html_print...
# knitr::kable(tab6B, format = "pipe")
html_print(HTML(kable(tab6B, "html")))

```

#### Table 6, Panel C: Wages (ln_real_qp1_job)

```{r}
#| label: Table6PanelC
#| message: false

tab6C <- etable(list(m6C1, m6C2, m6C3, m6C4, m6C5, m6C6),
       se.below = TRUE,
       signif.code = c("***"=0.01,"**"=0.05,"*"=0.10," "=1),
       dict = dict_common, order = order_common, digits = 3,
       drop = "Intercept", fitstat = ~n + r2, tex = FALSE)

## for rendering: knitr...  for interactive: html_print...
# knitr::kable(tab6C, format = "pipe")
html_print(HTML(kable(tab6C, "html")))

```

## Replication of table 7

### Create the models

```{r}
#| label: table7Models
#| message: false

df_sub <- df %>%
  filter(!is.na(successful))

# Table 7 Panel A

m7A1 <- feols(
  ln_emp_manu_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m7A2 <- feols(
  ln_emp_manu_pop ~ successful + post + meventperyear |
    fips + non_us_t + int_l + aa_assass + aa_armed + aa_bomb +
    aa_facility + ww_firearm + ww_explo + ww_incend + year + month,
  cluster = ~fips, data = df_sub
)

m7A3 <- feols(
  ln_emp_const_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m7A4 <- feols(
  ln_emp_const_pop ~ successful + post + meventperyear |
    fips + non_us_t + int_l + aa_assass + aa_armed + aa_bomb +
    aa_facility + ww_firearm + ww_explo + ww_incend + year + month,
  cluster = ~fips, data = df_sub
)

m7A5 <- feols(
  ln_emp_whole_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m7A6 <- feols(
  ln_emp_whole_pop ~ successful + post + meventperyear |
    fips + non_us_t + int_l + aa_assass + aa_armed + aa_bomb +
    aa_facility + ww_firearm + ww_explo + ww_incend + year + month,
  cluster = ~fips, data = df_sub
)


# Table 7 Panel B

m7B1 <- feols(
  ln_emp_retail_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m7B2 <- feols(
  ln_emp_retail_pop ~ successful + post + meventperyear |
    fips + non_us_t + int_l + aa_assass + aa_armed + aa_bomb +
    aa_facility + ww_firearm + ww_explo + ww_incend + year + month,
  cluster = ~fips, data = df_sub
)

m7B3 <- feols(
  ln_emp_services_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m7B4 <- feols(
  ln_emp_services_pop ~ successful + post + meventperyear |
    fips + non_us_t + int_l + aa_assass + aa_armed + aa_bomb +
    aa_facility + ww_firearm + ww_explo + ww_incend + year + month,
  cluster = ~fips, data = df_sub
)

m7B5 <- feols(
  ln_emp_finance_pop ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m7B6 <- feols(
  ln_emp_finance_pop ~ successful + post + meventperyear |
    fips + non_us_t + int_l + aa_assass + aa_armed + aa_bomb +
    aa_facility + ww_firearm + ww_explo + ww_incend + year + month,
  cluster = ~fips, data = df_sub
)


```

### Create table 7

#### Table 7, Panel A: Manufacturing, Construction, Wholesale

```{r}
#| label: Table7PanelA
#| message: false

tab7A <- etable(list(m7A1, m7A2, m7A3, m7A4, m7A5, m7A6),
       se.below = TRUE,
       signif.code = c("***"=0.01,"**"=0.05,"*"=0.10," "=1),
       dict = dict_common, order = order_common, digits = 3,
       drop = "Intercept", fitstat = ~n + r2, tex = FALSE)

## for rendering: knitr...  for interactive: html_print...
# knitr::kable(tab7A, format = "pipe")
html_print(HTML(kable(tab7A, "html")))

```

#### Table 7, Panel B: Retail trade, Services, Finance and RE

```{r}
#| label: Table7PanelB
#| message: false

tab7B <- etable(list(m7B1, m7B2, m7B3, m7B4, m7B5, m7B6),
       se.below = TRUE,
       signif.code = c("***"=0.01,"**"=0.05,"*"=0.10," "=1),
       dict = dict_common, order = order_common, digits = 3,
       drop = "Intercept", fitstat = ~n + r2, tex = FALSE)

## for rendering: knitr...  for interactive: html_print...
# knitr::kable(tab7B, format = "pipe")
html_print(HTML(kable(tab7B, "html")))

```

## Replication of table 8

### Create the models

First we have to calculate the ln of the housing index (assuming the variable in the data is the plain index).

```{r}
#| label: table8Models
#| message: false

df_sub <- df %>%
  filter(!is.na(successful)) %>% 
  mutate(ln_hh_index = 100 * log(housing_index))

# Panel A – Brodeur Table 6
m8A1 <- feols(
  ln_hh_index ~ post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m8A2 <- feols(
  ln_hh_index ~ successful + post + meventperyear |
    fips + year + month,
  cluster = ~fips, data = df_sub
)

m8A3 <- feols(
  ln_hh_index ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l,
  cluster = ~fips, data = df_sub
)

m8A4 <- feols(
  ln_hh_index ~ successful + post + meventperyear |
    fips + year + month + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m8A5 <- feols(
  ln_hh_index ~ successful + post + meventperyear |
    fips + month^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)

m8A6 <- feols(
  ln_hh_index ~ successful + post + meventperyear |
    fips + month^year + div_9_all^year + non_us_t + int_l +
    aa_assass + aa_armed + aa_bomb + aa_facility +
    ww_firearm + ww_explo + ww_incend,
  cluster = ~fips, data = df_sub
)


```

### Create table 8

#### Table 8, Panel A: ln(house price index)

```{r}
#| label: Table8PanelA
#| message: false

tab8A <- etable(list(m8A1, m8A2, m8A3, m8A4, m8A5, m8A6),
       se.below = TRUE,
       signif.code = c("***"=0.01,"**"=0.05,"*"=0.10," "=1),
       dict = dict_common, order = order_common, digits = 3,
       drop = "Intercept", fitstat = ~n + r2, tex = FALSE)

## for rendering: knitr...  for interactive: html_print...
# knitr::kable(tab8A, format = "pipe")
html_print(HTML(kable(tab8A, "html")))

```

## Check parallel trend assumption

Define year of attack (failed or successful)

```{r}
#| label: Year of event

# Step 1: Get the event year (first 0->1 edge in post) and success status for each county.
ev_info <- df %>%
  arrange(fips, year) %>%
  group_by(fips) %>%
  mutate(is_event_year = (post == 0) & lead(post) == 1) %>%
  summarise(
    event_year  = if (any(is_event_year, na.rm = TRUE)) min(year[is_event_year],
                                                 na.rm = TRUE) else NA_integer_,
    is_success  = if (any(is_event_year, na.rm = TRUE)) as.integer(any(
         successful1[is_event_year] == 1, na.rm = TRUE)) else NA_integer_) %>%
  ungroup()

df_es <- df %>%
  left_join(ev_info, by = "fips") %>%
  filter(!is.na(event_year)) %>%  # keep only fips with an event
  mutate(event_time = year - event_year)

df_es_win <- df_es %>% filter(event_time >= -3, event_time <= 3)

```

Plot to check parallel trend assumption

```{r}
#| label: iPlot
#| message: false

es_mod <- feols(
  ln_emp_pop ~ i(event_time, is_success, ref = -1) | fips + year,
  cluster = ~ fips,
  data = df_es_win)

iplot(es_mod,
      main = "Event study (successful vs failed): parallel-trend check",
      xlab = "Years relative to event (ref = -1)",
      ref.line = 0)
      
# tidy_es <- broom::tidy(es_mod, conf.int = TRUE) %>%
#   filter(str_detect(term, "^event_time::")) %>%
#   mutate(event_time = as.numeric(str_match(term, "event_time::(-?\\d+)")[,2]))

# 
# ggplot(tidy_es, aes(event_time, estimate)) +
#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
#   geom_point() +
#   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .2) +
#   labs(title = "Event study (successful − failed): parallel-trend check",
#        x = "Years relative to event (ref = −1)",
#        y = "Diff-in-diff effect on ln_emp_pop") +
#   theme_minimal()

```

### Interpretation

The pre-treatment coefficients (t = −3, −2) are close to zero and statistically indistinguishable from zero, supporting the parallel trend assumption.

Starting from t = +1, coefficients turn negative, suggesting that counties experiencing a successful attack face lower employment growth relative to counties with failed attacks, although estimates are imprecisely estimated.
